Pillar 2 - Topic Modeling

### 2019-01-16 Pillar 2 - Topic Modeling.Rmd
functions to prepare and visualize output of LDA

## Results

```{r function visualize_LDA, eval = F}
visualize_LDA <- function(results, id_plot = "test", facet = F, topic_names = NULL){

  # Beta distribution
  tidy(LDA_description_10, matrix = "beta") %>%
    mutate(topic = paste("Topic", topic)) %>%
    group_by(topic) %>%
      top_n(10, beta) %>%
    ungroup %>%

  ggplot(aes(x = reorder_within(term, by = beta, within = topic), y = beta, fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ topic, scales = "free") +
    scale_x_reordered() +
    labs(x = "Terms", y = "Beta", title = "Main Terms of each Topic") +
    coord_flip() +
    theme_light() +
    theme(plot.title = element_text(hjust = 0.5))

  # Gamma Distribution
  data_gamma <- tidy(LDA_description_10, matrix = "gamma") %>%
    mutate(topic = paste("Topic", topic)) %>%
    rename(Code = document) %>%
    left_join(select(d_course, Code, Cluster, Concentration, `Concentration (additional)`), by = "Code")

@@

  # Gamma Distribution: plot 1 docu-topic
  data_gamma %>%
    group_by(facet, topic) %>%
      summarise(gamma = sum(gamma))
    filter(gamma > 0.05) %>%
    ggplot(aes(reorder_within(facet, by = gamma, within = topic), y = gamma, fill = facet)) +
    geom_col(show.legend = F) +
    facet_rep_wrap(~ topic, scales = "free",
                   repeat.tick.labels = "bottom") +
    scale_x_reordered() +
    coord_flip() +
    labs(x = "(Group of) Courses", y = "Gamma", title = "Main Courses/Clusters of each Topic") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))

@@

  # Plot 2
  doc_topic %>%
    filter(gamma > 0.05) %>%
    ggplot(aes(reorder_within(topic, by = gamma, within = facet), y = gamma, fill = topic)) +
    geom_col(show.legend = F) +
    facet_rep_wrap(~ facet, scales = "free",
                   repeat.tick.labels = "bottom") +
    scale_x_reordered() +
    coord_flip() +
    labs(x = "Topics", y = "Gamma", title = "Main Topics of each Courses/Cluster") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))

@@

>>>>

## Results
```{r}
prepare_data_LDA_beta <- function(results) tidy(results, matrix = "beta") %>%
                                        mutate(topic = paste("Topic", topic)) %>%
                                          group_by(topic) %>%
                                            top_n(10, beta) %>%
                                          ungroup

prepare_data_LDA_gamma <- function(results, facet = Course){

  data_gamma <- tidy(results, matrix = "gamma") %>%
    mutate(topic = paste("Topic", topic)) %>%
    rename(Code = document) %>%
    left_join(select(d_course, Code, Cluster, Concentration, `Concentration (additional)`), by = "Code")

@@

  data_gamma <- data_gamma %>%
    group_by(facet, topic) %>%
      summarise(gamma = mean(gamma)) %>%
    filter(gamma > 0.05)
    ungroup

```{r function visualize_LDA, eval = F}
visualize_LDA_beta <- function(data_prepared, id_plot = "test"){

  data_prepared %>%
  ggplot(aes(x = reorder_within(term,
                                by = beta,
                                within = topic),
             y = beta,
             fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ topic, scales = "free") +
    scale_x_reordered() +
    labs(x = "Terms", y = "Beta", title = "Main Terms of each Topic") +
    coord_flip() +
    theme_light() +
    theme(plot.title = element_text(hjust = 0.5))

}

visualize_LDA_gamma1 <- function(data_prepared, id_plot = "test"){

  data_prepared %>%
    ggplot(aes(reorder_within(facet, 
                              by = gamma, 
                              within = topic), 
               y = gamma, 
               fill = facet)) +
    geom_col(show.legend = F) +
    facet_wrap(~ topic, 
               scales = "free") +
    scale_x_reordered() +
    coord_flip() +
   # labs(x = ensym(facet), y = "Gamma", title = paste("Main", ensym(facet), "of each Topic") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))

@@

}

visualize_LDA_gamma2 <- function(data_prepared, id_plot = "test"){???

  data_prepared %>%
    ggplot(aes(reorder_within(topic, 
                              by = gamma,
                              within = facet), 
               y = gamma, 
               fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ facet, 
               scales = "free") +
    scale_x_reordered() +
    coord_flip() +
  #  labs(x = "Topics", y = "Gamma", title = "Main Topics of each Courses/Cluster") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))

@@

}

```
